---
title: "week6_codealong"
author: "Cali Pfleger"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```


## Part 2: A rank-based test example (Mann Whitney U)

# make some mock unpaired data and investigate the difference in ranks (often called a medians comparison) by Mann-Whitney U using the wilcox.test() function  

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

#histograms
hist(gp_1)
hist(gp_2)

##we’ll perform Mann-Whitney U to answer “Is there a significant difference in ranks (medians) between gp_1 and gp_2?” using the wilcox.test() function.
my_mwu <- wilcox.test(gp_1, gp_2)

## call to get output
my_mwu

```

## Part 3: Simple linear regression
#We’ll exploring the relationship between two continuous variables, using the penguins dataset from the palmerpenguins package in R.

# A. exploratory scatterplot of penguing flipper length versus body mass
```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()

```


## B. model it using lm().

```{r}
# Linear model, stored as penguin_lm:
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

# Return the complete overview:
summary(penguin_lm)
```

## C. Access model outputs
### We can access the coefficients for the model using:
##The slope is 49.69 (g / mm)
##The y-intercept is -5780.83 (g)
##The full equation is mass = 49.69*(flipper length) + (-5780.83)
##But trying to get all of the statistical information from the summary() function would be kind of a mess.

## We can use the broom::tidy() function to get the model outputs in nice data frame format:

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

# Get the intercept: 
penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int


# Metrics at a glance: 
penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out

```



## D. Explore model assumptions
## Recall that we have assumptions for linear regression we need to explore, some related to the residuals.

### -Linearly related variables (CHECK - already looked & thought hard)
### - Normally distributed residuals
### - Homoscedasticity (constant residuals variance)
### - iid residuals (no serial correlation) - more often a concern in time series data

```{r}
plot(penguin_lm)

```


## E. Visualize the model
### Now that we’ve explore the assumptions and have decided that linear regression is a valid tool to describe the relationship between flipper length and body mass, let’s look at the model.

### - Use geom_smooth(method = "lm") to add a linear model to an existing scatterplot

### - Use stat_cor() and/or stat_regline_equation() to add equation information directly to the plot panel, at an x- and y-position that you specify (and yes, you can mess with the digits & appearance here)


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm",
              color = "red",
              size = 0.5,
              fill = "gray10",
              alpha = 0.5) +
  theme_light() +
  ggpubr::stat_regline_equation(label.x = 180, label.y = 5700)
```
## F. Find Pearson’s r for correlation:


```{r}
penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)

```

